\section*{\LARGE{Acknowledgements}}

Throughout the writing of this dissertation, I have received a great deal of support and assistance.

I would like to express my gratitude to my thesis supervisor, Assistant Professor Dr Elias Athanasopoulos, for his valuable guidance, encouragement and patient advice he provided me over the course of accomplishing my dissertation. During the past year, Dr Athanasopoulos interest, excitement and refined knowledge in the field of Cybersecurity has been undoubtedly a source of inspiration for me. All these have made my endeavour an exciting experience. He provided me with the tools that I needed to choose the right direction and successfully complete my dissertation.

Also, I would like to thank my fellow students Demetris Kaizer and Orpheas Van Rooy for their excellent teamwork and participation to a greater project that consists of each one's thesis. In addition, I would like to thank PhD candidate Michalis Papapevripides of SREC Lab for its continuous response to any issues that arose and for the assistance it provided me in resolving them.

Furthermore, I would like to thank all my professors who played a vital role in my academic accomplishments and from whom I received invaluable knowledge and helped me to become a Computer Scientist during my four years of study at the Department of Computer Science of the University of Cyprus.

Finally, I would like to thank my family and friends who supported me with love, understanding and supported me at every step.
