\chapter{Conclusion}
\label{sec:conclusion}
\vspace*{0.25cm}

Fuzzing has evolved significantly in analysing native applications, becoming a hot field for research. While it is used extensively to uncover destructive bugs and security vulnerabilities in native apps, web applications have received limited attention.

In this thesis, we presented \pname{}, a prototype open-source grey-box fuzzer for discovering Cross-Site Scripting vulnerabilities in web applications. \pname{} utilizes \emph{instrumentation} on the target web application for producing a \emph{feedback loop} and employing it to boost code coverage score. Consequently, it increases the total of potential vulnerabilities found.

For the evaluation of \pname{} we used two web applications; namely WordPress and Drupal, for the following three metrics: competence in detecting Reflected Cross-Site Scripting bugs, Throughput and Global Code Coverage.

Regarding the first metric, \pname{} was able to detect the most artificially injected vulnerabilities compared to the other three black-box fuzzers in the test. More specifically, it was able to weed out \emph{30} bugs followed by Wfuzz with \emph{28}. Secondly, in terms of throughput, unfortunately, for now, \pname{} does not match the throughput of native applications fuzzers such as AFL nor black-box web-app fuzzers such as Wfuzz as the overhead from the \emph{instrumentation} is hefty. Other outcomes in our third metric, suggest that our fuzzing tool can achieve coverage of the WordPress and Drupal codebase up to \emph{21.5\%} and \emph{27.3\%} respectively, in roughly 4 days of fuzzing.

Following a "borderline" rejection on the initial submission of this thesis at CODASPY 2021, the due modifications and clarifications were made, giving us confidence that a more comprehensive study will be accepted when resubmitted to DIMVA 2021 for publication.